100 Years of Social Work Research: A Data Science Perspective

### 2014-12-30 Analysis.Rmd
Updated figures. All code is working. Cleaning needed.

# Initialize workspace and functions for data wrangling

@@

# Read BWR functions for Mac OS
source("/Users/beperron/Git/BibWrangleR/functions/piWrangleR.R")
source("/Users/beperron/Git/BibWrangleR/functions/packages.R")

# Set the path where original raw data are stored
setwd("/Users/beperron/Git/SocialWorkResearch")

@@

@@

```{r initialization_analysis, message=FALSE, warning=FALSE, comment=NA}
rm(list=ls())
load("piArticles.R")
library(dplyr)
library(ggplot2)
library(gridExtra)

@@

```{r journal_lifespan}
#10 longest running journals 
longest.running <- n.so.yr %>%
       mutate(last = as.numeric(last), first = as.numeric(first), 
              year.diff = last - first) %>%
       arrange(desc(year.diff)) %>%
       select(title, first, last, year.diff)

head(longest.running, 10)

#10 shortest running journals
shortest.running <- longest.running %>% arrange(year.diff, first, last)
head(shortest.running, 20)
```

@@

# Print summary statistics in list form
subject.terms.l

@@

```{r subject_terms_overtime}
decade <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

@@

@@

# What are topic areas over time (by author specified keywords)?

```{r comment=NA, warning=FALSE, message=FALSE}
kp.df <- filter(pi.df, attributes == "KP")

@@

@@

# Location

@@

most.frequent

@@

## Location over time

keywords <- pi.df %>%
        filter(attributes == "LO") %>%
        select(articleID = articleID, keywords = record)

>>>>

# Initialize OS-X workspace and functions for data wrangling

@@

# Read BWR functions for Mac OS
source("/Users/beperron/Git/BibWrangleR/functions/piWrangleR.R")
source("/Users/beperron/Git/BibWrangleR/functions/packages.R")
# Set the path where original raw data are stored
setwd("/Users/beperron/Git/SocialWorkResearch")

@@

# Initialize Windows workspace and functions for data wrangling

@@

```{r initialization_analysis, message=FALSE, warning=FALSE, comment=NA}
rm(list=ls())
setwd("/Users/beperron/Git/SocialWorkResearch")
source("/Users/beperron/Git/BibWrangleR/functions/ggsurv.R")
load("piArticles.R")
library(dplyr)
library(ggplot2)
library(gridExtra)
library(survival)
library(grid)
library(png)

@@

```{r journal_lifespan}
#10 longest running journals 
longest.running <- n.so.yr %>%
       mutate(last = as.numeric(last), first = as.numeric(first), 
              year.diff = last - first) %>%
       arrange(desc(year.diff)) %>%
       select(title, first, last, year.diff) %>%
       mutate(stop = year.diff, event = ifelse(as.numeric(last) != 2014, 1, 0)) %>%
       select(title, stop, event, as.numeric(first))

survival.journals <- survfit(Surv(longest.running$stop+1, longest.running$event) ~ 1)
median.survival <- data.frame(time = c(12,12), quant = c(.5,0))

head(longest.running)

ggsurv(survival.journals) + 
    geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
    annotate("segment", x = 18, xend = 12, y = .12, yend = .15, size = .25, arrow =arrow()) +
    geom_text(x = 29, y =.12, label = "median survival", size = 4) + 
    geom_text(x = 75, y =.75, label = "+ = Last year in print", size = 4)

@@

@@

```{r subject_terms_overtime, warning=FALSE, message=FALSE}
decade <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

decade$year <- cut(decade$year, breaks = 10, labels = c(1:10))

@@

keywords.decade <- lapply(keywords.data.split, terms.f)
keywords.decade <- lapply(keywords.decade, unlist)

@@

# What are the most frequent topic areas (by author specified keywords)?

```{r keywords_overall, comment=NA, warning=FALSE, message=FALSE}
kp.df <- filter(pi.df, attributes == "KP")

@@

```{r keywords_over_time, warning=FALSE, message=FALSE}
decade <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

decade$year <- cut(decade$year, breaks = 10, labels = c(1:10))

@@

# Location of Studies

```{r location, comment=NA, warning=FALSE, message=FALSE}

@@

location <- arrange(most.frequent, desc(Freq))

print(subject.terms.l)

print(location)

img2 <- readPNG("/Users/beperron/Git/SocialWorkResearch/Chloro.png")
grid.raster(img2)
```

## Location of studies over time

```{r location_over_time, warning=FALSE, message=FALSE}

top.10.countries <- head(location, 10)
top.10.countries <- top.10.countries$subject.terms
top.10.countries <- levels(droplevels(top.10.countries))

year <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

location <- pi.df %>%
        filter(attributes == "LO") %>%
        select(articleID = articleID, keywords = record) %>%
        filter(keywords %in% top.10.countries)

location.year <- location %>% 
         left_join(year)

@@
